Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
picture and some text for the dynamic case

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}

@@

\newcommand{\skug}[1]{{\color{blue}[SK: #1]}}
\newcommand{\hmey}[1]{{\color{red}[HM: #1]}}
\newcommand{\AB}[1]{{\color{purple}[AB: #1]}}

@@

    \subsection{Results \skug{Full: 3, Polished: 2}}
    \subsubsection{Static experiments}
    \paragraph{Tiny cluster}

    On the tiny cluster, \heft could produce valid assignments in $14$ experiments out of $290$ ($4.8\%$).
    The successful schedules were achieved almost exclusively on the tiny workflows and one one 200-task workflow.
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm could schedule
    $94.9\%$ of workflows, thus having the smallest failure rate of $5\%$.

@@

    \subsubsection{Impact of cluster composition}
    On the {\em fat-and-thin} cluster, the baseline produces $60$\% invalid results on small workflows, $83.3$\% on
    middle-sized and $88.9$\% on big workflows, and therefore performs worse than on the normal cluster.

    The relative makespans are $14-29$\% worse for small workflows, $22-40$\% worse on middle-sized workflows and $16-35$\%
    on big workflows.
    \wrt failures, all heuristics again manage to schedule all workflows.
    \subsubsection{Behavior of workflow types when scaling workflow size}
    \subsubsection{Running times}
    The geometric means of runtimes of all heuristics on small workflows lie between $0.9$ and $2.2$ seconds.
    For middle-sized workflows, the runtimes for \heftbl and \heftblc are close to $2$ minutes, while \heftmm
    takes $5.1$ minutes.
    For the big workflows, again, \heftbl and \heftblc show a better runtime ($5$ and $5.4$ minutes, respectively).
    \heftmm takes $13.9$ minutes on average.
    \subsubsection{Dynamic experiments}
    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 20 experiments out of 290 ended with a valid makespan
    in case of \heftbl, 33 in case of \heftblc and 29 in case of \heftmm.
    In case of \heftmm, the makespan without recomputation would have been, on average, $5.77$ times longer than with the recomputation.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}
\usepackage{graphicx}

@@

\newcommand{\skug}[1]{{\color{blue}[SK: #1]}}
\newcommand{\hmey}[1]{{\color{red}[HM: #1]}}
\newcommand{\AB}[1]{{\color{purple}[AB: #1]}}
\newcommand{\willchange}[1]{{\color{orange}[AB: #1]}}

@@

    \subsection{Results \skug{Full: 3, Polished: 2}}

    \subsubsection{Preliminary experiments}

    Our preliminary experiments have shown that evicting large or small files does not give a notable change in makespan.

    \subsubsection{Static experiments}
    \paragraph{Tiny cluster}

    On the tiny cluster, \heft could produce valid assignments in $14$ experiments out of $290$ ($4.8\%$).
    The successful schedules were achieved exclusively on the tiny workflows (with only one 200-task size-increased
    workflow among them).
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm could schedule
    $94.9\%$ of workflows, thus having the smallest failure rate of $5.1\%$.

@@

    \subsubsection{Dynamic experiments}
    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan withjout recomputation. $13$ experiments ended with a valid makespan after recomputation in case of \heft,
   $16$ in case of \heftmm, $50$ in case of \heftblc and $55$ in case of \heftbl.
    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    There were valid final makespans with no recomputation only for the smallest workflows - $56$ original ones, $47$ 200-task ones,
    $25$ 1000-task ones and $6$ 2000-task ones.

    With growing size of the workflow, the excess makespan of not recomputing grows - from $13.9\%$ to $20\%$ for \heftbl,
    from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the 2000-task workflows in this case), $12.1\%$ to $23.5\%$
    for \heftmm.
    The larger variations for \heft can be explained by the small amount of data - for example, there were only 2 200-task
    workflows for this case.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.495\columnwidth] {images/UpdatesMss2}
        \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm for different . Smaller is better.}
        \label{fig:updates-ms}
        \vspace{-0.3cm}
    \end{figure}
